ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python

### 2016-08-29 doc/paper.tex
little fixes

\author{Noah Weninger \and Abram Hindle}

@@

However, the code may contain bugs due to the infancy of the project and the nonstandard ways we are
interfacing with SuperCollider. Users are encouraged to submit bug reports on the project's GitHub
page\footnote{\url{https://github.com/nwoeanhinnogaehr/ScPy}}.

>>>>

\author{Noah Weninger\footnote{\href{mailto:nweninge@ualberta.ca}{nweninge@ualberta.ca}}\hskip
0.75em and Abram
Hindle\footnote{\href{mailto:hindle1@ualberta.ca}{hindle1@ualberta.ca}}\\Department of Computing
Science\\University of Alberta\\Edmonton, Canada}

@@

Please note that the code may contain bugs due to the infancy of the project and the nonstandard
ways we are interfacing with SuperCollider. Users are encouraged to submit bug reports on the
project's GitHub page\footnote{\url{https://github.com/nwoeanhinnogaehr/ScPy}}.
